A survey of HTTP caching options on the open Semantic Web

### 2015-01-17 sanity/paper1.tex
Jurgen todos
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@999 43ef1190-90fd-4dd7-a769-d0121f02b80e

Caching has been given a prominent place in the foundational documents
of the World Wide Web. Out of the 6 documents that make up the HTTP
1.1 standard, RFC7234 \cite{rfc7234} is entirely devoted to the topic,
and RFC7232 \cite{rfc7232} defines conditional requests, which is also
important when constructing caches. As the former notes:
\begin{quote} 
  The goal of caching in HTTP/1.1 is to significantly improve
  performance by reusing a prior response message to satisfy a current
  request.
\end{quote}
Furthermore, the Architecture of the World Wide Web
\cite{Jacobs:04:AWW} discusses caching throughout, and the definition
of the Representational State Transfer (REST) architectural style
\cite{Fielding_2000_Architectural-Styles} is partly motivated from the
requirement to implement efficient caching. We also note that caching
in the Internet infrastructure, through so-called Content Delivery
Networks, is both a large business area and something that could
provide great value to the Semantic Web.

@@

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain fresh, i.e. how long it is permissible to use
it. Based on this, the client doesn't need to contact the server at
all to reuse a cached response, but this requires a commitment from
the content provider. The standard also gives the client an
opportunity to heuristically determine a time to live. RFC7232, on the
other hand, defines a protocol for asking the server if the cached
response is still fresh using conditional requests. This doesn't
burden the content provider with the task of estimating the time to
live beforehand, but then, it must be able to answer if the resource
has changed less expensively than serving the entire response. These
two approaches can be combined, as a client may ask if a response is
fresh after it has expired. A number of headers are relevant to the
problem, we recorded those in Table~\ref{tab:headers} in
Appendix~\ref{app:fetcher} but they were not all used in this
analysis.\todo{Structured walkthrough}

@@

A general caching approach is given in \cite{yang2011caching}.  In
\cite{umbrich2012hybrid}, the term caching was used in a different
sense than we do, they rather prefetched an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL
queries.

@@

\section{Methodology}

We want to find information resources on the Web, and examine HTTP
headers that may allow caching. We record headers recommended by
current standards, as well as obsoleted and non-standard
headers. Additionally, we examine the triples in the returned
information resources to see if there is information there that may be
used to calculate heuristic freshness.

@@

In both the cases of standard-compliant freshness time and for the
other promising features, the test reports \pvalue = 0.0001. We can
conclude that it is highly likely that some servers are better at
exposing cache headers than others. Unfortunately, since most
\httph{Server} headers only contain generic values, little can be
learnt about these implementations. We note, however, that DBPedia
exposes standards-compliant freshness time of 604800 seconds (i.e. 1
week) for both LOD and SPARQL endpoints.\todo{hall of fame?}

@@

The two most important headers to control caching are \httph{Expires}
and \httph{Cache-Control}. As shown in Table~\ref{tab:headers}, there
are also others. We found \httph{Pragma} in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogates} were not observed.

@@

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.

>>>>

Caching has been given a prominent place in the foundational documents
of the World Wide Web. Out of the 6 documents that make up the HTTP
1.1 standard, RFC7234 \cite{rfc7234} is entirely devoted to the topic,
and RFC7232 \cite{rfc7232} defines conditional requests, which is also
important when constructing caches. As the former notes:
\begin{quote} 
  The goal of caching in HTTP/1.1 is to significantly improve
  performance by reusing a prior response message to satisfy a current
  request.
\end{quote}
Furthermore, the Architecture of the World Wide Web
\cite{Jacobs:04:AWW} discusses caching throughout, and the definition
of the Representational State Transfer (REST) architectural style
\cite{Fielding_2000_Architectural-Styles} is partly motivated from the
requirement to implement efficient caching. We also note that caching
in the Internet infrastructure, through so-called Content Delivery
Networks, is both a large business area and something that could
provide great value to the Semantic Web.\todo{pitch it}

@@

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain fresh, i.e. how long it is permissible to use
it. Based on this, the client doesn't need to contact the server at
all to reuse a cached response, but this requires a commitment from
the content provider. The standard also gives the client an
opportunity to heuristically determine a time to live. RFC7232, on the
other hand, defines a protocol for asking the server if the cached
response is still fresh using conditional requests. This doesn't
burden the content provider with the task of estimating the time to
live beforehand, but then, it must be able to answer if the resource
has changed less expensively than serving the entire response. These
two approaches can be combined, as a client may ask if a response is
fresh after it has expired. A number of headers are relevant to the
problem, we recorded those in Table~\ref{tab:headers} in
Appendix~\ref{app:fetcher} but they were not all used in this
analysis.\todo{Structured walkthrough}\todo{Impact}

@@

A general caching approach is given in \cite{yang2011caching}\todo{explain} . In
\cite{umbrich2012hybrid}, the term caching was used in a different
sense than we do, they rather prefetched an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL
queries\todo{explain} .

@@

\section{Methodology}
\todo{Improve, big}
We want to find information resources on the Web, and examine HTTP
headers that may allow caching. We record headers recommended by
current standards, as well as obsoleted and non-standard
headers. Additionally, we examine the triples in the returned
information resources to see if there is information there that may be
used to calculate heuristic freshness.

@@

In both the cases of standard-compliant freshness time and for the
other promising features, the test reports \pvalue = 0.0001. We can
conclude that it is highly likely that some servers are better at
exposing cache headers than others. Unfortunately, since most
\httph{Server} headers only contain generic values, little can be
learnt about these implementations. We note, however, that DBPedia
exposes standards-compliant freshness time of 604800 seconds (i.e. 1
week) for both LOD and SPARQL endpoints.\todo{Where and how}

@@

The two most important headers to control caching are \httph{Expires}
and \httph{Cache-Control}\todo{move to intro}. As shown in Table~\ref{tab:headers}, there
are also others. We found \httph{Pragma} (archaic HTTP 1.0 header) in
287 responses, but except for two hosts, where they were superfluous,
they were only used to prohibit caching. \httph{Surrogates} were not
observed.

@@

In Figure~\ref{fig:hardall}\todo{axis and labels}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.
